---
title: "DryTortugas2012"
author: "Abby Benson"
date: "September 19, 2017"
output:
  github_document: default
  html_notebook: default
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dry Tortugas 2012
This notebook was created in response to a current iOBIS data harvest in which the Dry Tortugas 2012 dataset seems to have errors. The data used were downloaded from https://www1.usgs.gov/obis-usa/ipt/resource?r=drytortugasreefvisualcensus2012. 

I'm working against the DwC-A for the Dry Tortugas 2012 dataset and I'm not seeing the missing eventIDs. Here are some examples.

```{r include=FALSE}
library(readr)
event <- read_delim("~/OBIS/MBONs/Marine Sanctuaries/MBONMarineSanctuaries/ReefVisualCensus/2012DryTortugas/dwca-drytortugasreefvisualcensus2012-v1.3/event.txt",
"\t", escape_double = FALSE, trim_ws = TRUE)
occurrence <- read_delim("~/OBIS/MBONs/Marine Sanctuaries/MBONMarineSanctuaries/ReefVisualCensus/2012DryTortugas/dwca-drytortugasreefvisualcensus2012-v1.3/occurrence.txt",
"\t", escape_double = FALSE, trim_ws = TRUE)
```

Here is the event file, note no missing eventIDs
```{r event}
library(Hmisc)
describe(event$eventID)
describe(event$parentEventID)
```

Here is the occurrence file, note no missing eventIDs
```{r occurrence}
library(Hmisc)
describe(occurrence$eventID)
describe(occurrence$parentEventID)
```

But maybe it's just that they don't match so I'll check one of the ones that you gave me specifically: parentEventID PrimarySamplingUnit 441U:StationNumber 1:MapGridNumber 2569889

```{r occurrence2}
d <- occurrence[which(occurrence$parentEventID == 'PrimarySamplingUnit 441U:StationNumber 1:MapGridNumber 2569889'),]
describe(d$eventID)
describe(d$parentEventID)
```

Same thing for the event file
```{r event2}
e <- event[which(event$parentEventID == 'PrimarySamplingUnit 441U:StationNumber 1:MapGridNumber 2569889'),]
describe(e$eventID)
describe(e$parentEventID)
```